Alone Together: Compositional Reasoning and Inference for Weak Isolation

### 2017-07-08 evaluation.tex
Edits. URL added.

\begin{table*}[t]\small
\centering
\begin{tabular}{|c|c|c|c|}
  \hline
\textbf{Transaction}   & \textbf{Invariant} 
& \textbf{MySQL-Isolation} & \textbf{PostgreSQL-Isolation} \\ 
\hline
\multirow{4}{*}{\C{New\_Order} }  & $I_1$ 
& RC &  RC\\ 
&  $I_2$ &SER & RR \\
&  $I_3$ & SER  &  RR  \\
& $I_4$ & RC & RC   \\
\hline
\multirow{4}{*}{\C{Payment}}  & $I_1 $ 
& RC &  RC\\ 
&  $I_2$  &RC & RC \\
&  $I_3 $ & RC  &  RC  \\
& $I_4$  & RC & RC   \\
\hline
\multirow{4}{*}{\C{Delivery}}  & $I_1$  
& RC &  RC \\ 
&  $I_2$ &SER & RR \\
&  $I_3$ & SER  &  RR \\
& $I_4$  & RC & RC   \\
\hline
\end{tabular}
\caption{Various invariant violations witnessed for the TPC-C
  benchmark on MySQL and PostgreSQL}
\label{tab:tpcc-eval}
\end{table*}

To sanity-check the results of \tool, we conducted experiments with
the high-contention OLTP workload  on TPC-C aiming to explore the
space of correct isolation levels for different transactions. The
workload involves  a mix of all five TPC-C transactions executing
against a TPC-C database with 10 warehouses. Each warehouse has 10
districts, and each district serves 3000 customers. There are a total
of 5 transactions in TPC-C, and given that MySQL and PostgreSQL
support 3 isolation levels each, there are a total of $3^5 = 243$
different configurations of isolation levels for TPC-C transactions on
MySQL and PostgreSQL. We executed OLTP benchmark with all 243
configurations, and found 171 of them violating at least one invariant.
Table~\ref{fig:tpcc-eval} shows the summary of these results. As
expected, the isolation levels that \tool infers for the TPC-C
transactions do not result in invariant violations, either on MySQL or
on PostgreSQL.

>>>>

\begin{table*}[t]\small
\centering
\begin{tabular}{|c|c|c|c|}
  \hline
\textbf{Transaction}   & \textbf{Invariant} 
& \textbf{MySQL-Isolation} & \textbf{PostgreSQL-Isolation} \\ 
\hline
\multirow{4}{*}{\C{New\_Order} }  & $I_1$ 
& RC &  RC\\ 
&  $I_2$ &SER & RR \\
&  $I_3$ & SER  &  RR  \\
& $I_4$ & RC & RC   \\
\hline
% \multirow{4}{*}{\C{Payment}}  & $I_1 $ 
% & RC &  RC\\ 
% &  $I_2$  &RC & RC \\
% &  $I_3 $ & RC  &  RC  \\
% & $I_4$  & RC & RC   \\
% \hline
\multirow{4}{*}{\C{Delivery}}  & $I_1$  
& RC &  RC \\ 
&  $I_2$ &SER & RR \\
&  $I_3$ & SER  &  RR \\
& $I_4$  & RC & RC   \\
\hline
\end{tabular}
\caption{Various invariant violations witnessed for the TPC-C
  benchmark on MySQL and PostgreSQL}
\label{tab:tpcc-eval}
\end{table*}

To sanity-check the results of \tool, we conducted experiments with
the high-contention OLTP workload  on TPC-C aiming to explore the
space of correct isolation levels for different transactions. The
workload involves  a mix of all five TPC-C transactions executing
against a TPC-C database with 10 warehouses. Each warehouse has 10
districts, and each district serves 3000 customers. There are a total
of 5 transactions in TPC-C, and given that MySQL and PostgreSQL
support 3 isolation levels each, there are a total of $3^5 = 243$
different configurations of isolation levels for TPC-C transactions on
MySQL and PostgreSQL. We executed the OLTP workload on the TPC-C
benchmark with all 243 configurations, and found 171 of them violating
at least one invariant.  Table~\ref{fig:tpcc-eval} shows the summary
of these results. As expected, the isolation levels that \tool infers
for the TPC-C transactions do not result in invariant violations,
either on MySQL or on PostgreSQL.

### 2017-07-08 implementation.tex
Edits. URL added.

type district = {d_id: int; d_next_o_id: int}
type order = {o_id: int; o_d_id: int; o_c_id: int; o_ol_cnt: int}
type order_line = {ol_o_id: int; ol_d_id: int; ol_i_id: int; ol_qty: int}
type stock = {s_i_id: int; s_d_id:int; s_qty: int}
\end{ocaml}
\caption{OCaml type definitions corresponding to the TPC-C schema from
Fig.~\ref{fig:schema1}}
\label{fig:ocaml-schema}
\end{figure}

We have implemented our DSL to define transactions as monadic
computations in OCaml (modulo the syntactic sugar), and our automatic
reasoning framework as an extra frontend pass (called \tool) in ocamlc
4.03 compiler\footnote{The source code is available at available at
\emph{\ldots}}. The input to \tool is a program in our DSL that
describes the schema of the database as a collection of OCaml type
definitions, and transactions as OCaml functions, whose top-level
expression is an application of the \C{atomically\_do} combinator to a
function of type $a \rightarrow \C{DB}\;b$, for some (base) types $a$
and $b$. For instance, TPC-C's schema from Fig.~\ref{fig:schema1} can
be described via the OCaml type definitions shown in
Fig.~\ref{fig:ocaml-schema}.  \tool also requires a specification of
the program in the form of a collection of guarantees ($G$), one per
transaction, and an invariant $I$ that is a conjunction of the
integrity constraints on the database. An auxiliary DSL that includes
the first-order logic (FOL) combinators has been implemented for this
purpose. \tool's verification pass follows OCaml's type checking pass,
hence the concrete artifact of verification is OCaml's typed AST. The
tool is already equipped with  an axiomatization of PostgreSQL and
MySQL's isolation levels expressed in our FOL DSL. Other data stores
can be similarly axiomatized. The concrete result of verification is
an assignment of an isolation level of the selected data store to each
transaction in the program.

>>>>

type district = {d_id: int; d_next_o_id: int}
type order = {o_id: int; o_d_id: int; o_c_id: int; o_ol_cnt: int}
type order_line = {ol_o_id: int; ol_d_id: int; ol_i_id: int; ol_qty: int}
type stock = {s_i_id: int; s_d_id:int; s_qty: int}
\end{ocaml}
\caption{OCaml type definitions corresponding to the TPC-C schema from
Fig.~\ref{fig:schema}}
\label{fig:ocaml-schema}
\end{figure}

We have implemented our DSL to define transactions as monadic
computations in OCaml (modulo the syntactic sugar), and our automatic
reasoning framework as an extra frontend pass (called \tool) in ocamlc
4.03 compiler\footnote{The source code is available at
\emph{https://goo.gl/nmUXZK}}. The input to \tool is a program in our DSL that
describes the schema of the database as a collection of OCaml type
definitions, and transactions as OCaml functions, whose top-level
expression is an application of the \C{atomically\_do} combinator to a
function of type $a \rightarrow \C{DB}\;b$, for some (base) types $a$
and $b$. For instance, TPC-C's schema from Fig.~\ref{fig:schema} can
be described via the OCaml type definitions shown in
Fig.~\ref{fig:ocaml-schema}.  \tool also requires a specification of
the program in the form of a collection of guarantees ($G$), one per
transaction, and an invariant $I$ that is a conjunction of the
integrity constraints on the database. An auxiliary DSL that includes
the first-order logic (FOL) combinators has been implemented for this
purpose. \tool's verification pass follows OCaml's type checking pass,
hence the concrete artifact of verification is OCaml's typed AST. The
tool is already equipped with  an axiomatization of PostgreSQL and
MySQL's isolation levels expressed in our FOL DSL. Other data stores
can be similarly axiomatized. The concrete result of verification is
an assignment of an isolation level of the selected data store to each
transaction in the program.
